%-------------------------
% Resume in Latex
% Author : Sajal Sharma
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sajal Sharma} \\ \vspace{1pt}
    \small +65 9077-9093 $|$ \href{mailto:contact@sajalsharma.com}{\underline{contact@sajalsharma.com}} $|$ 
    \href{https://linkedin.com/in/sajals}{\underline{linkedin.com/in/sajals}} $|$
    \href{https://github.com/sajal2692}{\underline{github.com/sajal2692}}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \resumeSubHeadingListStart
    \resumeSubItem{AI Engineer with 8+ years specializing in Applied AI, NLP, and Deep Learning. Proven track record of leading teams, building AI-first products across Asia, and teaching cutting-edge AI concepts as O'Reilly instructor and Yale guest lecturer. Deep expertise in LLMs, RAG systems, AI agents, and scalable Generative AI solutions.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {AI Engineer}{Jun 2024 -- Present}
    {Liminal (formerly Menyala, a Temasek-backed Venture Studio)}{Singapore}
    \resumeItemListStart
      \resumeItem{Spearheading AI innovation across Liminal's venture portfolio, architecting multi-agent systems including VC copilot for automated investment analysis and Matrix, an agentic search platform enabling AI agents to query and retrieve information across multiple data sources.}
      \resumeItem{Leading engineering team of 4 for Lana, developing an AI-based underwriting platform. Architecting end-to-end solution with Typescript/Next.js frontend, Python/FastAPI backend, LangGraph multi-agent workflows, automated data processing pipelines, task processing using Celery \& Redis, Supabase \& AWS integratio.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Lead AI Engineer}{Jan 2023 -- Jun 2024}
    {OneByZero}{Singapore}
    \resumeItemListStart
      \resumeItem{Led team of 6 engineers developing production-grade AI solutions using LLMs, RAG, vector databases, and agent-based systems, delivering enterprise implementations including banking chatbot and social media AI agent handling 3000+ posts for major Filipino companies.}
      \resumeItem{For Splore, a Temasek backed AI startup, led development of end-to-end search infrastructure combining semantic search, Langchain-powered Q\&A systems, and ranking function optimization, reducing incorrect responses by 50\%, tripling engagement, and improving MAP from 0.3 to 0.8.}
    \resumeItemListEnd
  
    \resumeSubheading
      {Senior Machine Learning Engineer}{Aug 2017 -- Dec 2022}
      {Unscrambl}{India}
      \resumeItemListStart
        \resumeItem{Developed NLP capabilities for proprietary business analytics product including NER, text classification, and NL to SQL systems using NLTK, spaCy, and transformers, while building automated training data generation pipelines.}
        \resumeItem{Led design \& deployment of chatbot solutions for clients across Asia, impacting over 100,000 monthly users using Microsoft Bot Framework and Azure AI Services for NLU and dialog management.}
    \resumeItemListEnd

    % \resumeSubheading
    %   {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
    %     \resumeItem{Developed a game in Java to test the generated dungeons}
    %     \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
    %     \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
    %     \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
    %     \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Melbourne}{Melbourne, Australia}
      {Master of Information Technology, Major in Computing}{Aug 2014 -- Aug 2016}
    \resumeSubheading
      {Bharatiya Vidyapeeth University}{New Delhi, India}
      {Bachelor of Computer Applications}{Jul 2010 -- Jul 2013}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Applied AI}{: RAG, Multi-Agent Systems, AI Agents, Vector Databases, Langchain, Prompt Engineering, MCP} \\
     \textbf{Machine Learning}{: PyTorch, Huggingface, Sentence Transformers, BERT, SpaCy, NLTK} \\
     \textbf{Infrastructure \& Tools}{: AWS, GCP, Docker, Terraform, Git, Opensearch/Pinecone, PostgreSQL, Redis, Celery} \\
    }}
 \end{itemize}

%-----------ACTIVITIES & RECOGNITION-----------
\section{Activities \& Recognition}
\resumeItemListStart
  \resumeItem{\textbf{Instructor, O'Reilly (2025 - Present)}{: Created "Building AI Agents with LangGraph," a 3-hour video course on developing AI agents with Python, OpenAI, and LangGraph, covering multi-agent architectures and essential design patterns. Also teaching \href{https://learning.oreilly.com/live-events/agentic-rag-with-langgraph/0642572176174/}{\underline{"Agentic RAG with LangGraph"}}, a live course focused on building agentic RAG systems.} \\}
  \resumeItem{\textbf{Guest Lecturer, Yale University (2025)}{: Delivered guest lecture on "Building Agentic Systems with LangGraph" in MGT 899: Generative AI \& Entrepreneurship.} \\}
  \resumeItem{\textbf{Mentor \& Project Reviewer, Udacity (2017 - 2023)}{: Coached 100+ international students, recognized as elite mentor in 2021 with A+ performance grade. Reviewed 1,000+ projects across Data Science courses.} \\}
  \resumeItem{\textbf{Mentor, STEM Industry Mentoring Programme, University of Melbourne (2020 - 2023)}{: Mentored students in technology careers and academic development.} \\}
  \resumeItem{\textbf{Creator, Data Science Portfolio}{: GitHub repository with 1,000+ stars showcasing various Data Science projects.} \\}
\resumeItemListEnd


%-----------CERTIFICATIONS-----------
% \section{Certifications}
% \resumeItemListStart
%   \resumeItem{Natural Language Processing Nanodegree, Udacity}
%   \resumeItem{Deep Learning Specialization, DeepLearning.AI}
%   \resumeItem{Machine Learning Nanodegree, Udacity}
% \resumeItemListEnd

%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
